NeuronUnit: Collaborative Validation Testing of Neuroscientific Models

### 2013-11-28 NeurounitFrontiers/Paper.tex
Revamped abstract

\title[Running Title]{NeuronUnit: Collaborative Validation Testing of Neurophysiological Models}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
\topic{Python in Neuroscience II}% If your article is part of a Research Topic, please indicate here which.

@@

\begin{abstract}
Rigorously validating a scientific model's explanatory power requires comparing its predictions against empirical data on an ongoing basis. 
However, model validation remains an informal and incomplete process, especially in fields like neuroscience where the available data is growing rapidly.   
This has made it difficult to develop compare competing models, to determine the state-of-the-art, and to precisely identify open modeling problems.

Software engineers validate software by writing simple executable tests, called ``unit tests''. 
Suites of such unit tests can collectively provide evidence for its validity and correctness. 
Drawing inspiration from this practice, we develop the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
executable functions, here written in Python, that compare model predictions against a single empirical observation to produce a score indicating agreement between the model and the data. 
Suites of such validation tests are used as a summary of modeling progress within a scientific community. 
As a first application of this framework, we describe \textit{NeuronUnit}, a library that supports validation testing for neurophysiology and integrates with several existing neuroinformatics resources.

\tiny
 \keyFont{ \section{Keywords:} Neuroinformatics Simulation Electrophysiology Software Modeling } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

>>>>

\title[Running Title]{NeuronUnit: Collaborative Validation Testing of Neuroscientific Models}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
\topic{Python in Neuroscience II}% If your article is part of a Research Topic, please indicate here which.

@@

\begin{abstract}
Rigorously validating a quantitative scientific model requires comparing its predictions against an unbiased selection of experimental observations according to sound statistical criteria. Developing new models thus requires a comprehensive and contemporary understanding of competing models, relevant data and statistical best practices. Today, this can only be achieved by developing an encyclopedic knowledge of the literature. 
Unfortunately, in rapidly-growing fields like neuroscience, this has become increasingly untenable, even for the most conscientious scientists.

%However, today's model validation process is based on one-time peer review of a scientific publication. , and thus remains an informal and incomplete process, particularly in fields like neuroscience where the number of competing models and the volume of relevant data is growing rapidly.   
%This makes it difficult to determine community-accepted validation criteria, compare competing models,  determine the state-of-the-art given the latest experimental data, and to precisely identify open modeling problems.

Software engineers seeking to verify, validate and contribute to a complex software project rely not only on peer review, but on suites of simple executable tests, called ``unit tests''. 
Drawing inspiration from this practice, we have developed \textit{SciUnit}, a framework for developing ``model validation tests'' -- 
executable functions, here written in Python, that compare a quantitative model's predictions against a single experimental  observation to produce a score indicating agreement between the model and the data, as determined by a statistical test. 
Suites of such validation tests are collaboratively developed by a scientific community and can be used as a  summary of the state-of-the-art in a scientific community. In this paper, we aim to introduce this test-driven workflow to the neuroscience community. We proceed by describing \textit{NeuronUnit}, a library that builds upon \textit{SciUnit} and integrates with several existing neuroinformatics standards and resources to support validation testing of single-neuron models using data gathered by neurophysiologists.

\tiny
 \keyFont{ \section{Keywords:} Neuroinformatics Simulation Electrophysiology Software Modeling\todo{is this the right format for this?} } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}
